17th International Satisfiability Modulo Theories Competition (SMT-COMP 2022): Rules and Procedures

### 2022-06-23 rules/rules22.tex
Clarified rules for starexec configurations

\header{Participation in the Competition.}
%
For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available, or communicated separately to the
organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions which it enters} via the
web form at
\begin{center}
  \url{https://forms.gle/ewNQdFJbmQ12GxpX8}
\end{center}
For each track the submission must specify the logics which are
supported by the solver.  The solver will enter all divisions where it
supports at least one logic.  A submission \textbf{must} also include a
link to the \emph{system description} (see below) and a \emph{32-bit
  unsigned integer}.  These integer numbers, collected from all
submissions, are used to seed competition tools.

@@

\header{Input and output.}
Participating solvers will be connected to a trace executor, which
will incrementally send commands to the standard input channel of the
solver and read responses from both the standard output channel of the
solver.  The commands will be taken from an SMT-LIB benchmark script
that satisfies the requirements for incremental track scripts given in
Section~\ref{sec:logistics}.
%
Solvers must respond to each command sent by the trace executor with
the answers defined in the SMT-LIB format specification, that is, with
an answer of \texttt{sat}, \texttt{unsat}, or \texttt{unknown} for
\akey{check-sat} commands, and with a \texttt{success} answer for
other commands.
Solvers must not write anything to the standard error channel.

@@

\header{Trace Executor.} This track will use the trace executor
to execute a solver on an incremental benchmark file.

>>>>

\header{Participation in the Competition.}
%
For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available, or communicated separately to the
organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec
supports solver configurations.  You can have at most one configuration
for each track (named after the track) and a default configuration used
for tracks without a track-specific configuration.
Moreover, the organizers must be informed of the solver's presence
\emph{and the tracks and divisions which it enters} via the web form
at
\begin{center}
  \url{https://forms.gle/ewNQdFJbmQ12GxpX8}
\end{center}
For each track the submission must specify the logics which are
supported by the solver.  The solver will enter all divisions where it
supports at least one logic.  A submission \textbf{must} also include a
link to the \emph{system description} (see below) and a \emph{32-bit
  unsigned integer}.  These integer numbers, collected from all
submissions, are used to seed competition tools.

@@

\header{Input and output.}
Participating solvers should include a script
\texttt{smtcomp\_run\_incremental} (if this is not present the script
for the default configuration will be used). This script will be called
without arguments and will be connected to a trace executor, which
will incrementally send commands to the standard input channel of the
solver and read responses from both the standard output channel of the
solver.  The commands will be taken from an SMT-LIB benchmark script
that satisfies the requirements for incremental track scripts given in
Section~\ref{sec:logistics}.
%
Solvers must respond to each command sent by the trace executor with
the answers defined in the SMT-LIB format specification, that is, with
an answer of \texttt{sat}, \texttt{unsat}, or \texttt{unknown} for
\akey{check-sat} commands, and with a \texttt{success} answer for
other commands.
Solvers must not write anything to the standard error channel.

@@

\header{Trace Executor.} This track will use the trace executor from
{\url{https://github.com/SMT-COMP/trace-executor}}
to execute a solver on an incremental benchmark file.
